---
title: "Simple document"
output: html_document
---

```{r}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

# Section 3
### Plot from last time

This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot.

<!--eval=FALSE, message=FALSE, echo=FALSE-->

```{r chunk_scatterplot} 
plot_df=
  tibble(
    x=rnorm(n=1000),
    y=1+2*x^2+rnorm(n=1000)
  )
ggplot(plot_df,aes(x=x,y=y))+geom_point()
```

```{r chunk_histogram}
ggplot(plot_df,aes(x=x))+geom_histogram()
```

### Plot for learning assessment

This is a quick kind of solution to the LA!
```{r}
la_df=
  tibble(
    norm=rnorm(n=500,mean=1),
    logical=norm>0,
    abs_norm=abs(norm)
  )
  ggplot(la_df,aes(x=abs_norm))+geom_histogram()
```

Here's a list:

* list item 1
* list item 2
